Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-09-06 Papers/ms.tex
Mention residuals
residual sentence

@@

>>>>

{\revisions
For the sampled parameter values representing the posterior distribution, there
was no structure in the residuals (not shown), when normalised by the noise
standard deviation in each pixel. This is unsurprising since the model
assumptions are entirely correct for this dataset.
}

@@

{\revisions
As with the easy dataset, the standardised residuals of the sampled models
resembled noise.
}
